### 2016-05-20 intro.tex
more complaining :)

\section{Introduction}
\paragraph{Basic issues in Naor-Yogev. }
\begin{itemize}
\item The NY paper formalizes and investigates a security notion of limited interest
\item The proposed construction won't scale in common network applications
\item The main results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters!
\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.  This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.
\end{itemize}

@@

Finally, the Bloom filter formalization that is given does not obviously capture traditional Bloom filters!  Traditionally, both Bloom filter population and querying procedures use hash functions $h_1,h_2,...h_k$ that each map from some universe $U$ to $[m]$, where $m$ is the bit-length of the array $M$ that represents a given set $S$.  These hash functions are missing from the authors’ definition, apparently swept into the algorithms $B_1$ (population) and $B_2$ (querying).  I don't really understand how, though. They allow $B_1$ to be randomized, which would let $B_1$ pick the hash functions.  But the security definition provides no way for $B_1$ to share these with $B_2$.  So how would $B_2$ be able to process set-membership queries?  (Note: based on how they define the size of the representation M, $B_1$ cannot include descriptions of $h_1, h_2, \ldots , h_k$ in $M$.  They really mean $M$ to be the array that represents the set $S$.)  In general, their formalization of the Bloom filter primitive is badly underdefined.

@@

\tsnote{Perhaps.  I'm still not convinced.  If you read the text preceding the statement of Theorem 1.2 (page 4), you'll see their discussion of lower bounds on “memory” required for a given set size and FP rate.  This bound is the classical one for Bloom filters and speaks only of the (bit)size of the array.  It says nothing about the description of the hash functions needed to populate the array.  In fact, this lower bound is for any method of representing set $S$ in a bit array, not only for hashing-based methods.
%
Maybe they are defining “memory” differently in this discussion than in their theorems.  This would be annoying, and I think it isn't the case.  So for the moment, I'll continue to hold my position on this.
%
(I'll also point out that they explicitly say that $B_1$ outputs “compressed representation of [set $S$] $B_1(S)=M$”.  But it would be easy to have small sets $S$ for which the bitsize of the array is smaller than the total bitsize of $S$, yet the combined bitsize of array + hash functions is larger.)
%
But for the sake of argument, say that their representation size m does include the description of the hash functions.  To me, this is a clunky way to handle this matter.  For one thing, it doesn't play well with analysis in the ROM, which is the traditional way to establish results relating FP rate, set size and array size for Bloom filters.  (I know there are standard model assumptions that suffice, too.)  For another, this way of accounting makes unnecessarily hard to answer the two important operational questions: how big is the array, and how many hash function calls do I need to make per item/query?  
% 
I'll agree that this syntactic issue does not matter for theorem statements such as “...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…”  In fact, this statement would be true for the traditional way of defining Bloom filter memory (array size), since the extra space is basically for a PRP key.}

>>>>

\section{Introduction}
\paragraph{Basic issues in Naor-Yogev. }
\begin{itemize}
\item The NY paper formalizes and investigates a security notion of limited interest
\item The proposed construction won't scale in common network applications
\item The main results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters!
\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.  This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.  (If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.)
\item Not sure what Bloom filter-like data structures would have randomized querying procedures (``unsteady representations'').  They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.  But what's the purpose of this, if the security definition gives the adversary the set~$S$?  (What are you keeping private?) 
\end{itemize}

@@

Finally, the Bloom filter formalization that is given does not obviously capture traditional Bloom filters!  Traditionally, both Bloom filter population and querying procedures use hash functions $h_1,h_2,...h_k$ that each map from some universe $U$ to $[m]$, where $m$ is the bit-length of the array $M$ that represents a given set $S$.  These hash functions are missing from the authors’ definition, apparently swept into the algorithms $B_1$ (population) and $B_2$ (querying).  I don't really understand how, though. They allow $B_1$ to be randomized, which would let $B_1$ pick the hash functions.  But the security definition provides no way for $B_1$ to share these with $B_2$.  So how would $B_2$ be able to process set-membership queries?  (Note: based on how they define the size of the representation $M$, $B_1$ cannot include descriptions of $h_1, h_2, \ldots , h_k$ in $M$.  They really mean $M$ to be the array that represents the set $S$.)  In general, their formalization of the Bloom filter primitive is badly underdefined.

@@

\tsnote{Perhaps.  I'm still not convinced.  If you read the text preceding the statement of Theorem 1.2 (page 4), you'll see their discussion of lower bounds on “memory” required for a given set size and FP rate.  This bound is the classical one for Bloom filters and speaks only of the (bit)size of the array.  It says nothing about the description of the hash functions needed to populate the array.  In fact, this lower bound is for any method of representing set $S$ in a bit array, not only for hashing-based methods.
%
Maybe they are defining “memory” differently in this discussion than in their theorems.  This would be annoying, and I think it isn't the case.  So for the moment, I'll continue to hold my position on this.
%
(I'll also point out that they explicitly say that $B_1$ outputs “compressed representation of [set $S$] $B_1(S)=M$”.  But it would be easy to have small sets $S$ for which the bitsize of the array is smaller than the total bitsize of $S$, yet the combined bitsize of array + hash functions is larger.)
%
But for the sake of argument, say that their representation size~$m$ does include the description of the hash functions.  To me, this is a clunky way to handle this matter.  For one thing, it doesn't play well with analysis in the ROM, which is the traditional way to establish results relating FP rate, set size and array size for Bloom filters.  (I know there are standard model assumptions that suffice, too.)  For another, this way of accounting makes unnecessarily hard to answer the two important operational questions: how big is the array, and how many hash function calls do I need to make per item/query?  
% 
I'll agree that this syntactic issue does not matter for theorem statements such as ``...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…''.  In fact, this statement would be true for the traditional way of defining Bloom filter memory (array size), since the extra space is basically for a PRP key.}
